\chapter{Conclusion and Future Work}

\section{Summary}
	The overall goal of this project was to optimize respiratory navigator gating to improve the clinical utility of spiral cine DENSE cardiac MRI for the quantification of cardiac mechanics. To accomplish this goal, we completed three separate respiratory-related experiments: 1) we determined how using a respiratory navigator affects the reproducibility of measures of cardiac mechanics, 2) we determined the optimal respiratory navigator gating configuration, and 3) we developed an interactive respiratory-controlled videogame for the purpose of improving navigator efficiency.
	
\subsection{Experiment 1}
	
	The purpose of the first experiment was to understand how using a respiratory navigator during DENSE cardiac MRI can affect the derived cardiac mechanics. This experiment was separated into two different studies. In the first study, we examined how strain is affected by using a respiratory navigator. Specifically, we wanted to determine if normal inconsistency in end-expiratory diaphragm position between separate image acquisitions significantly affects estimates of cardiac strains. Strain varies longitudinally throughout the heart \cite{Kuijer2002,Moore2000,Young1994a,Feng2009,NasiraeiMoghaddam2010,Donekal2013a,Suever2017} and patients struggle to hold their breath consistently \cite{Liu1993,Wang1995a,Taylor1997a,Holland1998c,Fischer2006a}. Thus, we hypothesized that inconsistent end-expiratory positions during image acquisition would lead to differences and variability in measured strain and using a respiratory navigator would result in less variable strain measurements.
	
	Analysis was performed in 10 healthy volunteers (Age: 22 $\pm$ 6 years, 60\% female) including seven patients with heart disease (Age: 57 $\pm$ 8 years, 43\% female). To simulate end-expiratory position inconsistency, DENSE images were each acquired at the patient-specific minimum, middle, and maximum end-expiratory positions; a repeated acquisition at the middle position was used to quantify variability independent of end-expiratory differences. The range of end-expiratory positions across 10 breath-holds was 10 $\pm$ 4 mm. There were no significant differences in global or regional peak radial, circumferential, or longitudinal strains measured at the different end-expiratory positions (p = 0.17-–0.98). In general, there were also no differences in variability in global or regional peak strains between inconsistent (minimum, middle, and maximum) and consistent (two acquisitions from middle position) end-expiratory positions (p = 0.10-–0.95). In summary, this study demonstrated that \textit{measurements of left ventricular peak strains with DENSE cardiac MR are relatively insensitive to normal changes in end-expiratory position between separate image acquisitions.} Importantly, this indicates that using a respiratory navigator to ensure a consistent end-expiratory position is not required for acquisitions used to derive strains.
	
	In the second study, we examined how variability in torsion is affected by using a respiratory navigator. Torsion is computed using a basal and apical image acquired during \textit{separate} end-expiratory breath-holds and the assumption that the distance between images remains constant. However, because patients typically struggle to achieve a consistent end-expiratory position for multiple image acquisitions \cite{Liu1993,Wang1995a,Taylor1997a,Holland1998c,Fischer2006a}, this inconsistency could lead to variability in the derived torsion measurement. Since torsion has been shown to be limited by high variability \cite{Donekal2013a}, we hypothesized that this variability was partly due to inconsistent end-expiratory positions during serial image acquisition, which could be significantly improved by using a respiratory navigator for cardiac MRI-based quantification of torsion. We assessed respiratory-related variability in 10 healthy volunteers (Age: 22 $\pm$ 6 years, 60\% female) including seven patients with heart disease (Age: 57 $\pm$ 8 years, 43\% female). Using DENSE cardiac MRI, we acquired multiple basal and apical images during 2 scenarios: 1) \textit{enforced} end-expiratory position variability and 2) \textit{natural} end-expiratory position variability. In the first scenario, the inter-test variability of torsion was compared between consistent and inconsistent end-expiratory positions. In the second scenario, the inter-test variability was compared between breath-holds and navigator-gated scans. From the first scenario, enforced variability in end-expiratory position translated to considerable variability in measured torsion (0.56 $\pm$ 0.34$^{\circ}$/cm), whereas inter-test variability with consistent end-expiratory position was 57\% lower (0.24 $\pm$ 0.16$^{\circ}$/cm, p $<$ 0.001). From the second scenario, natural respiratory variability from consecutive breath-holds translated to a variability in torsion of 0.24 $\pm$ 0.10$^{\circ}$/cm, which was significantly higher than the variability from navigator-gated scans (0.18 $\pm$ 0.06$^{\circ}$/cm, p = 0.02). By using a respiratory navigator with DENSE, theoretical sample sizes to detect a clinically meaningful change in torsion were reduced from 66 to 16 and 26 to 15, by using a respiratory navigator, as calculated from the two experiments. This study demonstrated that \textit{a substantial portion (22-57\%) of the inter-test variability of torsion can be reduced by using a respiratory navigator to ensure a consistent breath-hold position between image acquisitions.}

\subsection{Experiment 2}
	The purpose of experiment 2 was to determine the optimal respiratory navigator gating configuration for the quantification of left ventricular strain using spiral cine DENSE MRI. Two-dimensional spiral cine DENSE was performed using two single-navigator configurations (retrospective, prospective) and a combined “dual-navigator” configuration in 10 healthy adults (Age: 23 $\pm$ 3 years, 40\% female) and 20 healthy children  (Age: 13 $\pm$ 3 years, 45\% female. The adults also underwent breath-hold DENSE as a reference standard for comparisons. Peak left ventricular strains, signal-to-noise ratio (SNR), and navigator efficiency were compared. Subjects also underwent dual-navigator gating with and without visual feedback to determine the effect on navigator efficiency. There were no differences in circumferential, radial, and longitudinal strains between navigator-gated and breath- hold DENSE (P = 0.09-–0.95). The dual configuration maintained SNR compared with breath-hold acquisitions (16 versus 18, P = 0.06). SNR for the prospective configuration was lower than for the dual navigator in adults (P = 0.004) and children (P $<$ 0.001). Navigator efficiency was higher (P $<$ 0.001) for both retrospective (54\%) and prospective (56\%) configurations compared with the dual configuration (35\%). Visual feedback improved the dual configuration navigator efficiency to 55\% (P $<$ 0.001). This study demonstrated: \textit{1) when quantifying left ventricular strains using spiral cine DENSE MRI, a dual navigator configuration results in the highest SNR in adults and children, 2) in adults, a retrospective configuration has good navigator efficiency without a substantial drop in SNR, 3) prospective gating should be avoided because it has the lowest SNR, and 4) visual feedback represents an effective option to maintain navigator efficiency while using a dual navigator configuration.}
	
\subsection{Experiment 3}
	The purpose of experiment 3 was to develop and test an interactive videogame to improve navigator efficiency in children undergoing DENSE cardiac MRI. Advanced cardiac MRI acquisitions often require long scan durations that necessitate respiratory navigator gating. The tradeoff of navigator gating is reduced scan efficiency, particularly when the patient's breathing patterns are inconsistent, as is commonly seen in children. We hypothesized that engaging pediatric participants with a navigator-controlled videogame to help control breathing patterns would improve navigator efficiency and maintain image quality. We developed custom software that processed the Siemens respiratory navigator image in real-time during CMR and represented diaphragm position using a cartoon avatar, which was projected to the participant in the scanner as visual feedback. The game incentivized children to breathe such that the avatar was positioned within the navigator acceptance window ($\pm$3 mm) throughout image acquisition. Fifty children (Age: 14 $\pm$ 3 years, 48\% female) with no significant past medical history underwent a respiratory navigator-gated 2D spiral cine DENSE cardiac MRI acquisition first with no feedback (NF) and then with the feedback game (FG). Thirty of the 50 children were randomized to undergo extensive off-scanner training with the FG using a MRI simulator, or no off-scanner training. Navigator efficiency, signal-to-noise ratio (SNR), and global left-ventricular strains were determined for each participant and compared. Using the FG improved average navigator efficiency from 33 $\pm$ 15 to 58 $\pm$ 13\% (P $<$ 0.001) and improved SNR by 5\% (P = 0.01) compared to acquisitions with NF. There was no difference in navigator efficiency (P = 0.90) or SNR (P = 0.77) between untrained and trained participants for FG acquisitions. Circumferential and radial strains derived from FG acquisitions were slightly reduced compared to NF acquisitions (−16 $\pm$ 2\% vs −17 $\pm$ 2\%, P $<$ 0.001; 40 $\pm$ 10\% vs 44 $\pm$ 11\%, P = 0.005, respectively). There were no differences in longitudinal strain (P = 0.38). This study demonstrated that \textit{use of a respiratory navigator feedback game during navigator-gated CMR improved navigator efficiency in children from 33 to 5\%. This improved efficiency was associated with a 5\% increase in SNR for spiral cine DENSE. Extensive off-scanner training was not required to achieve the improvement in navigator efficiency.}
	
	
\section{Clinical Implications}
	The goal of this project was to optimize respiratory navigator gating for use during DENSE cardiac MRI. Importantly, we learned it's best "use" cases. From the first experiment, it was demonstrated that the quantification of peak left ventricular cardiac strains is relatively insensitive to normal variations in end-expiratory positions between image acquisitions. In the clinical setting, since there were no differences in peak strain between end-expiratory positions, patient end-expiratory diaphragm position does not have to be monitored when performing breath-hold DENSE acquisition for single image analyses. These findings should generalize to other image acquisitions that are used to derive measures of cardiac strains.
	
	However, the second study on the variability of torsion demonstrated that using a respiratory navigator \textit{significantly} improves the variability of measured torsion. These findings have meaningful implications for future cardiac MRI-based quantification of LV torsion in the clinical setting. First, acquisition of LV torsion data using a respiratory navigator should be employed, where feasible, to minimize variability. This approach is not typical in the majority of published papers reporting torsion and may reduce clinical feasibility of such data acquisition; however, the additional effort appears justified by the considerable reduction in variability. If inconsistency in end-expiratory position is not addressed with the data acquisition, then it is important to incorporate effects of in- consistent end-expiratory position into the assessment of the standard error of measurement for LV torsion, which will substantially increase needed sample sizes for research trials or reduce prognostic value for individual subjects.
	
	% need clinical implications for optimal navigator configuration
	
	Importantly, the equipment needed to utilize the FG is minimal and does not directly integrate into an imaging sequence; it connects externally to the scanner user interface. Due to the minimal equipment needed and non-invasive connection to the MRI scanner, we antici- pate that the FG system can be easily adopted at research and clinical sites that perform CMR navigator gating, especially in children. Since navigator efficiency can be increased from 33 to 58\%, leading to reduced acquisition times, use of the FG can help improve the clinical feasibility of advanced imaging techniques. While reducing the acquisition time would likely be the most common use of increased navi- gator efficiency from the FG, the saved time could be al- located to improve image spatial or temporal resolution [5]. Importantly, pre-scan training was not necessary for navigator efficiency improvement with our system, so clinical and research sites would not have to invest in an MRI simulator environment or spend significant time training children. Navigator feedback has been shown to reduce acquisition time in adults [5], thus, the use of the FG will likely work well in adults also. Since we only acquired DENSE images for this study,
	the specific findings are only definitively relevant for DENSE. However, it is reasonable to expect that these findings are generalizable to many other CMR acquisi- tions that utilize a respiratory navigator. Possible excep- tions include higher resolution applications, such as coronary MR angiography, which may be more sensitive to registration issues. Further study is needed to test this technique for these applications.
	
\section{Future Directions}

\subsection{Variability in cardiac mechaniscs}
	In Chapter 2, we used a respiratory navigator to measure and acquire DENSE cardiac images. Since a respiratory navigator restricts data acquistion to a narrow window, we could not measure the effect of inconsistent end-expiratory position \textit{during} breath-holds on the derived cardiac strains. It would be important to quantify variability in end-expiratory position during breath-hold DENSE cardiac MRI aquisition and examine whether the changes in strain values correspond to the magnitude of variability in end-expiratory position.
	
	Also in Chapter 2, we only examined differences and variability in strains due to inconsistent breath-hold positions in a small patient population. It would be beneficial to see if these results remain the same for a larger patient group with more heterogeneous contraction patterns. In particular, patients who have infarcted regions may have large gradient in strain from an infarcted to non-infarcted region. So, it would be beneifical to examine the
	
	 
	Chapters 2 and 3 demonstrated that variability torsion, but not strain, could be significantly imporved by using a respiratory navigator to ensure a consistent position between image acquisition.
	
	% chapter 2
	This study examined the effects of inconsistent end-expiratory positions on cardiac strains in a small patient sample. It would be beneficial to investigate this effect in a larger patient sample who have heterogeneous contraction patterns, for example, due to post-myocardial infarction. These patients may have steeper gradients in strain across infarcted to non-infarcted tissue regions [39]. Therefore, we cannot definitively say that the effects of inconsistent end-expiratory positions in that setting are similarly small and negligible. Future studies should investigate strain variability due to inconsistent end-expiratory positions in patients who have infarcted tissue in specific regions (e.g. anterior vs inferior).
	
	% chapter 3
	We examined the effects of variable end-expiratory position on LV torsion in a small patient sample. It may be beneficial to examine these results in a larger, more heterogeneous patient sample to determine whether specific diseases affect the results more than others, especially conditions that affect a patient’s ability to repeatedly hold his or her breath reproducibly (for example, pulmonary diseases). Due to the lengthy duration of DENSE breath-holds
	(~20 s) and their limitations in breath-holding ability, the breath-hold acquisition protocol was not performed in patients. Based on these factors, we expect that pa- tients would demonstrate higher variability in LV torsion with the breath-hold measures compared to the healthy volunteers we studied. Hence, the potential reduction in mean variability when using the respiratory navigator may in fact be higher than the 22% we report from the healthy volunteers in experiment 2. Nevertheless, the re- duction in LV torsion variability patients will achieve by using a respiratory navigator will likely fall between the study’s reported values of 22 and 57%.
	
	% combo chapters 2 and 3 future directions
	
\subsection{Optimal Navigator Configuration}
	% rewrite
	A third limitation of this study is the lack of assess-
	ment of clinical patients. Cardiac patients, who routinely undergo MR imaging and who may have limited ability to hold their breath, may not be able to perform the lengthy breathhold scan and may not achieve as high navigator effi- ciency when performing a dual navigator scan with feed- back. However, because this population is more likely to undergo DENSE MR imaging than this study’s volunteer subjects, it would be beneficial to determine whether the results remain the same. For example, it may be important to use dual navigator gating, even at the expense of naviga- tor efficiency, to achieve higher SNR, because SNR is com- monly lower in the clinical patient population compared with healthy volunteers.
	
\subsection{Interactive Videogame}

	% re-write this
	We performed this study in children with no significant past medical history. While we did attempt to re- cruit from a broad clinical population using recruitment services at our Center for Clinical and Translational Science, the population we ultimately studied may not be entirely representative of a standard pediatric clinical population that would routinely undergo cardiac MRI. For example, approximately 25 % of patients with tetral- ogy of Fallot may have learning and behavioral difficul- ties [23], which may impair their ability to benefit from the feedback game. It is therefore reasonable to expect that the true benefit of the feedback game in a standard clinical population will be smaller than what was mea- sured in the current study, but still better than what can be expected without the use of feedback. Even if only half of the patients benefit to the extent shown in the current study, the overall navigator efficiency for the clinical population as a whole would still increase from 33 % efficiency to 46 % efficiency (a 38 % relative bene- fit). Future research will seek to evaluate this in further detail as we implement the feedback game during rou- tine clinical workflows.
	
	Distribute videogame to research sites. have them use in patients since we only measure things in healthy subects
	
	- children who have duchense muscular distrophy
	- adults with heart disease and failure
	see if same conclusions hold.
	
	re-design videogame using more general, free (and not expensive license-based software) so that it can be distrbuted easier
	
	incorporate videogame into siemens scanner itself as an option instead of regular respiratory navigator
	
\subsection{Final Thoughts}
	
	