% acknowledgements

\phantomsection
\setcounter{page}{3} % set page number to 'iii'

\begin{center}
	\addcontentsline{toc}{part}{Acknowledgments}
	ACKNOWLEDGMENTS
\end{center}

\indent As in the dedication, I want to thank my wife. Throughout this entire process, including all of my education, she has pushed me forward and supported me in more ways than I can count. This dissertation is a summary of the work I've completed. I sincerely appreciated her support, especially since a lot my time was spent with my eyes glued to the computer screen at home or gone from home all together. This was the hardest thing I've ever completed and her support was what got me through it.

\indent Although this research was completed with my individual effort, its progress could not have been completed without the efforts of several people. I'd like to thank...

\begin{enumerate}
	\item Brandon Fornwalt - Brandon has always been very motivating and passionate about the overall goals in his lab, which was definitely something that drew me to him. He's always thinking about how we can improve. Most importantly, he's always pushing us to do our best work and I sincerely appreciate that. He's also focused on making sure that his graduate students work on impactful and exciting projects and looked for any way he could help. I'll always appreciate that about him. I'm happy to have been a part of his lab, which has shaped my thoughts and perspectives as well as pushed me to be a better researcher.
	\item Chris Haggerty - I sincerely appreciate the time Chris has taken to work with me on my projects and publications. He was always there to answer any questions about my ideas for experiments and analysis as well as to help me solidify my thoughts on paper.
	\item Jonathan Suever - I enjoyed having the opportunity to get to know Jonathan and his extensive programming knowledge (which I'm working to get to). Whether it was talking about the technical details of how to implement an idea or discussing the appropriate hardware/software for the job, I enjoyed learning from and with him.
	\item Greg Wehner - Greg and I have been through this entire process together as graduate students. It's been a long road and we've both definitely grown from it. Greg and I had the opportunity to lean on each other when we needed help. More importantly, Greg and I have become good friends. Although he is moving on to finish his MD degree and I am moving on to be a software engineer, I hope our paths cross again someday.
	\item David Powell - Dave has dealt with teaching me about MRI in the classroom and informal settings along with troubleshooting problems with our scans. Dave has been so helpful with everything MRI (which is pretty much everything that we do in this lab). I can't thank him enough for his kindness and wish him the best.
	\item Jonathan Grabau - I've had the pleasure of working with Grabau for a couple years in the Fornwalt lab. Personally, I can't thank him enough for spending all his time working to help me with my videogame project. Jonathan was responsible for the high throughput of children volunteers we were able to scan for the videogame project. I'm grateful for this helpfulness along with his friendship.
	\item Moriel Vandsburger - Moriel has always been something I can discuss food with (and I am a lover of food). Moreover, Moriel is a great person who really cares to help out. I sincerely appreciated him working with Greg and I to keep our projects going at UK, which allowed both of us to stay. I can't thank him enough for that and wish him the best of luck at Berkeley.
	\item Darin Cecil - Darin has been extremely helpful in making sure Greg and I don't have to deal with all the paperwork with our grants and funding. Darin has always been willing to help out me with a problem (no matter how small). I sincerely thank Darin for his helpfulness.
	\item Tanya Graf - Tanya has done so much behind and in front of the scenes to make sure my life as a graduate student and researcher goes smoothly. She was always someone I could come to with a problem and she would know immediately how or who could solve it. I sincerely appreciate her kindness and helpfulness.
	\item Other labmates - Linyuan Jing, Sam Fielden, David van Maanen, Chris Nevius, Arichanah Pulenthiran, and other labmates have been extremely helpful with reviews of my work and critiques of projects and presentations. Most importantly, I've appreciated the overall friendliness, helpfulness, and drive of everyone. Brandon and the lab does a great job of selecting fantastic candidates.I wish them and future labmates, good luck.
	\item Kevin Donohue - I'd like to thank Dr. Donohue for being my Master's advisor, which allowed me the opportunity to meet Brandon and eventually become a graduate student in his lab. I've always appreciated Dr. Donohue's guidance and helpfulness in the entirety of the graduate student process as well as for serving as co-Chair on my committee.
	\item Laurence Hassebrook - I would like to thank Dr. Hassebrook for serving on my committee as well as for his insightful comments about the training system for the videogame project.
	\item Abhijit Patwardhan - I'd like to thank Dr. Patwardhan for serving on my committee and for being a great teacher. I enjoyed learning in his class and about his thought processes.
	\item Gabe Dadi - Thank you for serving as external examinder on my committee for my defense.
\end{enumerate}
